---
title: "BrainButler"
output: html_document
---

# P100

Found significant differences at 80ms for TP10 & AF7 for Dark v. Non-Dark. Additional electrodes are statistially significant if you remove participants 8 and 3.

This aligns with previous findings. "Brain computer interface using flash onset and offset visual
evoked potentials"

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plotly)
library(data.table)
library(hrbrthemes)
library("ggpubr")

#Subsetting https://www.statmethods.net/management/subset.html

n100 <- fread("../erps/n100.txt")
fact <- n100[ which(n100$Type=='Fact' & n100$Participant!='p8' & n100$Participant!='p3'), ]
procedure <- n100[ which(n100$Type=='Procedure' &  n100$Participant!='p8' & n100$Participant!='p3' ), ]
dark <- n100[ which(n100$Type=='Dark'), ]
light <- n100[ which(n100$Type=='Light'), ]
factClean <- n100[ which(n100$Type=='Fact No Stimuli' & n100$Participant!='p8' & n100$Participant!='p3'), ]
procedureClean <- n100[ which(n100$Type=='Procedure No Stimuli' & n100$Participant!='p8' & n100$Participant!='p3'), ]

tone <- n100[ which(n100$Type=='Tone' & n100$Participant!='p8' & n100$Participant!='p3'), ]
noTone <- n100[ which(n100$Type=='No Tone' & n100$Participant!='p8' & n100$Participant!='p3'), ]

factMean <- mean(fact$TP9)
procedureMean <- mean(procedure$TP9)
darkMean <- mean(dark$TP9)
lightMean <- mean(light$TP9)

#wilcox.test(dark$TP9, light$TP9)
#wilcox.test(dark$TP10, light$TP10)
#wilcox.test(dark$AF7, light$AF7)
#wilcox.test(dark$AF8, light$AF8)
t.test(dark$TP9,light$TP9)
t.test(dark$TP10,light$TP10)
t.test(dark$AF7,light$AF7)
t.test(dark$AF8,light$AF8)
#ggdensity(light$TP9,  main = "dark$TP9", xlab = "X")


#wilcox.test(fact$TP9, procedure$TP9)
#wilcox.test(fact$TP10, procedure$TP10)
#wilcox.test(fact$AF7, procedure$AF7)
#wilcox.test(fact$AF8, procedure$AF8)
#t.test(fact$TP9,procedure$TP9)
#t.test(fact$TP10,procedure$TP10)
#t.test(fact$AF7,procedure$AF7)
#t.test(fact$AF8,procedure$AF8)

#wilcox.test(factClean$TP9, procedureClean$TP9)
#wilcox.test(factClean$TP10, procedureClean$TP10)
#wilcox.test(factClean$AF7, procedureClean$AF7)
#wilcox.test(factClean$AF8, procedureClean$AF8)
#t.test(factClean$TP9,procedureClean$TP9)
#t.test(factClean$TP10,procedureClean$TP10)
#t.test(factClean$AF7,procedureClean$AF7)
#t.test(factClean$AF8,procedureClean$AF8)

#wilcox.test(tone$TP9, noTone$TP9)
#wilcox.test(tone$TP10, noTone$TP10)
#wilcox.test(tone$AF7, noTone$AF7)
#wilcox.test(tone$AF8, noTone$AF8)
t.test(tone$TP9,noTone$TP9)
t.test(tone$TP10,noTone$TP10)
t.test(tone$AF7,noTone$AF7)
t.test(tone$AF8,noTone$AF8)

```
P600 Analysis

Interesting peak around 600ms for No stimuli fact and no stimulus procedure. However, no statistical significance was found. Additional control studies needed. 

```{r}
p600 <- fread("../erps/p600.txt")
fact <- p600[ which(p600$Type=='Fact No Stimuli' & p600$Participant!='p8' & p600$Participant!='p3'), ]
procedure <- p600[ which(p600$Type=='Procedure No Stimuli' & p600$Participant!='p8' & p600$Participant!='p3'), ]
ggdensity(fact$AF8,  main = "fact$AF8", xlab = "X")
ggdensity(procedure$AF8,  main = "procedure$AF8", xlab = "X")
t.test(fact$AF8,procedure$AF8)
factMean <- mean(fact$AF8)
procMean <- mean(procedure$AF8)

```


```{r}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plotly)
library(data.table)
library(hrbrthemes)

n100_dark_p2 <- fread("../erps/n100_p2_dark.txt")
n100_light_p2 <- fread("../erps/n100_p2_light.txt")
tp9_p2_dark <- n100_dark_p2$TP9
tp9_p2_light <- n100_light_p2$TP9
af7_p2_dark <- n100_dark_p2$AF7
af7_p2_light <- n100_light_p2$AF7
af8_p2_dark <- n100_dark_p2$AF8
af8_p2_light <- n100_light_p2$AF8
tp10_p2_dark <- n100_dark_p2$TP10
tp10_p2_light <- n100_light_p2$TP10

darkDat <- data.frame(x = rep(1:dim(n100_dark_p2)[1]), type = rep("dark", dim(n100_dark_p2)[1]), tp9 = tp9_p2_dark, af7 = af7_p2_dark, af8 = af8_p2_dark, tp10 = tp10_p2_dark)

lightDat <- data.frame(x = rep(1:dim(n100_light_p2)[1]), type = rep("light", dim(n100_light_p2)[1]), tp9 = tp9_p2_light, af7=af7_p2_light, af8=af8_p2_light, tp10=tp10_p2_light)

fullData <- rbind(darkDat, lightDat)

ggplot(fullData, aes(x=x, y=tp9, color=type)) + geom_point(shape=1)
ggplot(fullData, aes(x=x, y=af7, color=type)) + geom_point(shape=1)
ggplot(fullData, aes(x=x, y=af8, color=type)) + geom_point(shape=1)
ggplot(fullData, aes(x=x, y=tp10, color=type)) + geom_point(shape=1)

```
# P200

```{r}
# OLD


bins <- fread("../erplab_events/brain_butler_bins_n100.txt")

# Dark Events
tp9_dark = bins$bin3_TP9
tp10_dark = bins$bin3_TP10
af7_dark = bins$bin3_AF7
af8_dark = bins$bin3_AF8

# Non Dark
tp9_non_dark = bins$bin4_TP9
tp10_non_dark = bins$bin4_TP10
af7_non_dark = bins$bin4_AF7
af8_non_dark = bins$bin4_AF8

# Tone
tp9_tone = bins$bin5_TP9
tp10_tone = bins$bin5_TP10
af7_tone = bins$bin5_AF7
af8_tone = bins$bin5_AF8

# No Tone
tp9_no_tone = bins$bin6_TP9
tp10_no_tone = bins$bin6_TP10
af7_no_tone = bins$bin6_AF7
af8_no_tone = bins$bin6_AF8

# No Tone

if(FALSE) {
  erpData <- data.frame(bins$V33, tp9_dark, tp9_non_dark)
  fig <- plot_ly(erpData, x = ~bins$V33, y = ~tp9_dark, type = 'bar', name = 'TP9 Dark')
  fig <- fig %>% add_trace(y = ~tp9_non_dark, name = 'TP9 Non-Dark')
  fig <- fig %>% layout(yaxis = list(title = 'Voltage'), barmode = 'group')
  fig
}

plotDifferences <- function(eventA, eventB, rowIDs, colIDs, yAxisLabel) {
  erpData <- data.frame(rowIDs, eventA, eventB)
  colnames(erpData) <- colIDs
  fig <- plot_ly(erpData, x = ~rowIDs, y = ~eventA, type = 'bar', name = colIDs[2])
  fig <- fig %>% add_trace(y = ~eventB, name = colIDs[3])
  fig <- fig %>% layout(yaxis = list(title = yAxisLabel), barmode = 'group')
  fig
}

columnLabels = c("Participants","Dark", "No Dark")

# Run Dark Analysis

if (FALSE) {
  print("====Visual====")
  plotDifferences(tp9_dark, tp9_non_dark, bins$V33, columnLabels,"Voltage")
  plotDifferences(tp10_dark, tp10_non_dark, bins$V33, columnLabels,"Voltage")
  plotDifferences(af7_dark, af7_non_dark, bins$V33, columnLabels,"Voltage")
  plotDifferences(af8_dark, af8_non_dark, bins$V33, columnLabels,"Voltage")
  print("AF7")
  wilcox.test(af7_dark, af7_non_dark, paired = TRUE)
  print("AF8")
  wilcox.test(af8_dark, af8_non_dark, paired = TRUE)
  print("TP9")
  wilcox.test(tp9_dark, tp10_non_dark, paired = TRUE)
  print("TP10")
  wilcox.test(tp9_dark, tp10_non_dark, paired = TRUE)
}



#plotDifferences(tp9_tone, tp9_no_tone, bins$V33, columnLabels,"Voltage")
if (FALSE) {
  print("====Auditory====")
  print("AF7")
  wilcox.test(af7_tone, af7_no_tone, paired = TRUE)
  print("AF8")
  wilcox.test(af8_tone, af8_no_tone, paired = TRUE)
  print("TP9")
  wilcox.test(tp9_tone, tp9_no_tone, paired = TRUE)
  print("TP10")
  wilcox.test(tp10_tone, tp10_no_tone, paired = TRUE)
  
  plotDifferences(tp9_tone, tp9_no_tone, bins$V33, columnLabels,"Voltage")
  plotDifferences(tp10_tone, tp10_no_tone, bins$V33, columnLabels,"Voltage")
}

#print(erpData)


#print(positiveLatency$bin1_T9)
#hist(positiveLatency$bin1_T9)


#print(negativeLatency)

#summary(cars)
#library(data.table)
```
#Spectral Analysis
```{r}
spectral <- fread("../spectral_analysis/spectral.txt")
channel <- "AF8"

# Filter by channel and type
fact <- spectral[ which( spectral$Electrode==channel &  spectral$Type=='B8' & spectral$Participant!='p8' & spectral$Participant!='p3'), ]
procedure <- spectral[ which( spectral$Electrode==channel & spectral$Type=='B9' & spectral$Participant!='p8' & spectral$Participant!='p3'), ]



f = fact$Beta
p = procedure$Beta

t.test(f,p)
ggdensity(f,  main = "fact$beta", xlab = "X")
ggdensity(p,  main = "procedure$beta", xlab = "X")

meanFact <- mean(f)
meanProc <- mean(p)

```

